---
title: 'Product design: Imported beers'
author: "D"
date: "17 agosto 2016"
output: html_document
---

See bottom of document for credits.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
mirror = 'http://cran.us.r-project.org'
setwd("C:/Nuova cartella/Udemy Modelling Customers' Choices/Imported Beers")

```

```{r}
if (!require(knitr)) {
    install.packages("knitr", repos = mirror, dependencies = TRUE)
    require(knitr)
    library(knitr)
}

if (!require(conjoint)) {
    install.packages("conjoint", repos = mirror, dependencies = TRUE)
    require(conjoint)
    library(conjoint)
}

```

Product features are defined by seven factors ("origin", "Price", ...) each with 3 values ("levels")
```{r}
factors_list <- list(
  
  Origin = c("European", "Canadian", "Japanese"),
  Price = c("6.19","5.49","4.79"),
  Body = c("Rich full bodied","Regular","Crisp and clear"),
  Aftertaste = c("strong","mild", "very mild"),
  Calories = c("full", "regular", "low"),
  Packaging = c("Six 12Oz Large", "Six 12Oz Small",   "Four 16Oz"),
  Glass = c("Green Label",    "Brown Label",  "Brown Painted")  
  
)
print(factors_list)
kable(as.data.frame(factors_list))

```

This builds a data frame with all combinations of the factor values. Each is called "profile" and represents a (possibly illegal) product configuration.
```{r}
profiles <- expand.grid(factors_list)
str(profiles)
```

Number of profiles is clearly overwhelming, even for a small number of factors and factor levels. In our case, we have the following factors and number of levels:
```{r}
lengths_vector = sapply(factors_list, function (l) length(l))
lengths_data_frame = as.data.frame(lengths_vector)
names(lengths_data_frame) = c("Num. of Levels")
kable(lengths_data_frame)

```

This totals up to $`r prod(lengths_vector)`$ number of profiles. As a matter of fact, expand.grid function, whose size is: $`r dim(profiles)`$ gave us all of them:
```{r}
head(profiles)
kable (as.data.frame(profiles))

```

```{r}
design<-caFactorialDesign(data = profiles, type = "fractional", cards = 21)
str(design)
head(design)

```

Factor levels' descriptions are loaded from a file:
```{r}
levels = read.csv("levels.csv")
print(levels)

```

Eventually we get the answers from respondents:
```{r}
answers <- read.csv("preferences.csv")
str(answers)
head(answers)

```

CREDITS
Analytics Vidhya (www.analyticsvidhya.com) for data and procedures.